---
title: "demo"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE}
rm(list=ls(all=TRUE))
library(foreach)
library(kableExtra)

setwd("C:\\Users\\willi\\OneDrive - Yale University\\Desktop\\research\\hybrid platform design\\resubmission\\code")

source("mem functions.R")
```

#### Historical data
Assume there are three historical controls. Each has a sample size of 120, with a observed
probability of response of 0.19, 0.09 and 0.11, respectively. 
```{r, echo=FALSE}
his_trial <- data.frame(trial = 1:3, x = c(23, 11, 13), n = c(120, 120, 120),
                        y = c(97, 109, 107))

kable(his_trial) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```

#### Historical response rate
```{r, echo=FALSE}
his_trial$x/his_trial$n
```

#### Calibrate MEM to meet the upper limit of borrowing 
Assume the internal control (IC) has a sample size of 30 and the maximum amount of
borrowing allowed from the historical controls is 30. 
```{r, echo=FALSE}
## sample size of the internal control
n0 <- 30
## we plan to borrow at most 30 patients
n0_star <- 30
## set the target sample size
target_N <- n0+n0_star

mem_prior <- find.mem.prior(n_c = n0, hdat = his_trial, target_N = target_N )

H <- nrow(his_trial)
fit0 <- set.mem.prior(num_study = H+1, delta = mem_prior)

tab1 <- cbind(fit0$part, fit0$prior)
colnames(tab1) <- c("H1","H2", "H3", "IC", "Prior")
kable(tab1) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```

#### implement MEM
Assume there are 1, 2, ... 16 responses out of the 30 patients in IC
```{r, echo=FALSE}
## number of responses out of n0 patients
x0 <- seq(1, 16, 1)
## initial prior for the response rate of internal control
beta_a <- beta_b <- 1

mem_out <- NULL

for(i in 1:length(x0)){
  fit <- update.part.bin(x = c(his_trial$x, x0[i]), 
                         n = c(his_trial$n, n0), 
                         prior_part = fit0$prior, 
                         part = fit0$part)
  rstar <- fit$post_sim
  astar <- beta_a + sum(rstar*his_trial$x) + x0[i]
  bstar <- beta_b + sum(rstar*his_trial$y) + n0-x0[i]
  
  est <- qbeta(c(0.025, 0.5, 0.975), astar, bstar)
  ## effective sample size
  en <- astar + bstar
  
  mem_out <- rbind(mem_out, c(x0[i], est, en))
}
colnames(mem_out) <- c("# responses", "MEM_2.5CI", "MEM_Median", "MEM_97.5CI", "MEM_ESS")
```

#### Analyze the same data using a uniform prior for the response rate of internal control
```{r, echo=FALSE}
uni_out <- NULL
for(i in 1:length(x0)){
  est <- qbeta(c(0.025, 0.5, 0.975), 1+x0[i], 1+n0-x0[i])
  uni_out <- rbind(uni_out, est)
}
rownames(uni_out) <- NULL
colnames(uni_out) <- c("UNI_2.5CI", "UNI_Median", "UNI_97.5CI")

kable(round(cbind(mem_out, uni_out), 3)) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```
